### 2014-02-27 paper/relatedwork.tex
removed .pdf from repo, added some references

>>>>

\subsection{Misc}
\bjoern{These may not belong in related work, but I'm just collecting them here.}
\begin{itemize}
\item \cite{Wong-cgf11} - Wong presents a graph-based approach for generating continuous line illustrations from images. It's approach of linking edges into a continuous line based on Semi-Eulerization is similar to ours. Prior work used tours of nodes, rather than edges, and cast continuous line drawing as a traveling salesman problem~\cite{Bosch-tsp}.
\item \cite{Schweikardt-tei09} Schweikardt et al. also made a connection between electroluminescent wire and graph theory, though their contribution is orthogonal: they provide a tangible construction kit with smart nodes for building physical graph examples. Edges are lit up by EL wire.
\item \cite{strattman1997neon} - Strattman is the standard "text book" for neon lighting designers.
\item In neon sign making, segments of a tube that should not appear illuminated are covered with opaque paint. This is called "blocking out"\footnote{\url{http://en.wikipedia.org/wiki/Neon_sign}}.
\end{itemize}
